### 2015-09-09 fundamentals/impl.tex
A variety of small changes:
* tighten up somewhat redundant API discussion
* there appears to be a missing RIF antecedent
* improve implied causality of preference adjustment

\gls{ABM} is inherently object-oriented because agents represent discrete,
independently acting objects.  Figure \ref{fig:framework} illustrates the
modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator creates
a set of classes on which agent plug-ins are based.  Agent plug-ins utilize the
generic core \gls{API} to interact with one another.  For example, they use the
resource exchange paradigm \gls{API} for trading resources with one another.

Due to this plug-in architecture,
implementations of agents in a given scenario can be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be compared to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle.

Interchangeability is accomplished by providing inheritable \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction. For example,
an archetype that inherits the \Class{Region} interface, as in Figure
\ref{fig:agent_uml}, is interchangeable with any other Region agent.
For the archetype developer, this interface provides enormous power
very simply. The \gls{API} abstracts away unnecessary detail while providing
all necessary functionality for interacting with the \Cyclus simulation kernel.

@@

\Cyclus provides a novel representation of entities in the nuclear fuel cycle
that reflects the reality in international nuclear power: facilities implementing individual fuel cycle technologies, institutions managing those facilities, and regions providing geographical and political context for institutions and facilities. While
few simulators have provided any notion of static regional
effects \cite{huff_next_2010,juchau_modeling_2010}, \Cyclus allows for both regions and institutions to be first-class
agents in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by inheriting from the appropriate class.
\Cyclus implements a \gls{RIF} relationship through the
parent-child hierarchy described in \S \ref{sec:interchangeability}, where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a directed acyclic graph (DAG),
with regions as root nodes and facilities as leaf nodes.

Two primary consequences arise from this structure. First, institutions are
nominally responsible for deploying and decommissioning facilities. Accordingly, advanced
logic regarding building and decommissioning can be implemented on top of
those behaviors inherited from the
\Class{Institution} interface. Second, the \Class{Facility} class implements the
\Class{Trader} interface, and thus institutions and regions, respectively, can
adjust the resource flow preferences of their managed facilities. Importantly,
this capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).

>>>>

\gls{ABM} is inherently object-oriented because agents represent discrete,
independently acting objects.  Figure \ref{fig:framework} illustrates the
modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator creates
a set of classes on which agent plug-ins are based.  Agent plug-ins utilize the
generic core \glspl{API} that define agent-to-agent interaction as well as agent-to-environment interaction.
For example, they use the
resource exchange paradigm \gls{API} for trading resources with one another.  
For the archetype developer, these interfaces provide enormous power
very simply. The \gls{API} abstracts away unnecessary detail while providing
all necessary functionality for interacting with the \Cyclus simulation kernel.
For the user, multiple archetypes that inherit the same \glspl{API} are interchangeable
in a simulation.

Critically, this novel functionality enables the comparison
between agent implementations. For example, 
an archetype that inherits the \Class{Region} interface, as in Figure
\ref{fig:agent_uml}, is interchangeable with any other Region agent.

@@

\Cyclus provides a novel representation of entities in the nuclear fuel cycle
that reflects the reality in international nuclear power: facilities implementing individual fuel cycle technologies, institutions managing those facilities, and regions providing geographical and political context for institutions and facilities. While
few simulators have provided any notion of static regional
effects \cite{huff_next_2010,juchau_modeling_2010}, \Cyclus allows for both regions and institutions to be first-class
agents in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by inheriting from the appropriate class.
\Cyclus implements a \gls{RIF} relationship through a
parent-child hierarchy where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a directed acyclic graph (DAG),
with regions as root nodes and facilities as leaf nodes.

Two primary consequences arise from this structure. First, institutions are
nominally responsible for deploying and decommissioning facilities. Accordingly, advanced
logic regarding building and decommissioning can be implemented on top of
those behaviors inherited from the
\Class{Institution} interface. Second, the \Class{Facility} class implements the
\Class{Trader} interface to participate in resource exchange, and institutions and regions, respectively, can
adjust the resource flow preferences of their managed facilities. Importantly,
this capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).
